### 2025-03-18 Paper/Paper_draft1.tex
Updates from Overleaf

    There are several requirements for two hospitals to be affiliated through board members. First, and most relevant, there must be at least one shared board member on each hospital's board of directors. Second, hospitals must be within the same market to be considered affiliated by board member. For these purposes, I define a market as a Hospital Referral Region (HRR), defined by (fill in details here). I focus on markets since the outcomes of interest capture changes in competative behavior, which is most salient within the same market. Furthermore, it is much less likely for two different hospital board members in the same HRR to share an identical name. Finally, I focus on affiliations that are not due to being in the same system or network. Whether the hospital is independent or part of a system, I only consider board connections with hospitals that are independent or associated with a separate hospital system. Of the (blank) hospitals in the sample, almost 10\% are affiliated with another hospital through a shared board member. As shown in Figure \ref{fig:connected_percent}, this percentage remains constant over time.

    \begin{figure}[ht!]
        \centering
        \includegraphics[width=.7\textwidth]{Objects/connected_percent.pdf}
        \label{fig:connected_percent}
    \end{figure}

@@

    \begin{figure}[ht!]
        \centering
        \includegraphics[width=.7\textwidth]{Objects/connected_independent_HRR_percent.pdf}
        \label{fig:connected_HRR_percent}
    \end{figure}

>>>>

    There are several requirements for two hospitals to be affiliated through board members. First, and most relevant, there must be at least one shared board member on each hospital's board of directors. Second, hospitals must be within the same market to be considered affiliated by board member. For these purposes, I define a market as a Hospital Referral Region (HRR), defined by (fill in details here). I focus on markets since the outcomes of interest capture changes in competitive behavior, which is most salient within the same market. Furthermore, it is much less likely for two different hospital board members in the same HRR to share an identical name. Finally, I focus on affiliations that are not due to being in the same system or network. Whether the hospital is independent or part of a system, I only consider board connections with hospitals that are independent or associated with a separate hospital system. Of the (blank) hospitals in the sample, almost 10\% are affiliated with another hospital through a shared board member. As shown in Figure \ref{fig:connected_percent}, this percentage remains constant over time.

    \begin{figure}[ht!]
        \centering
        \includegraphics[width=.8\textwidth]{Objects/connected_percent.pdf}
        \label{fig:connected_percent}
    \end{figure}

@@

    \begin{figure}[ht!]
        \centering
        \includegraphics[width=.8\textwidth]{Objects/connected_HRR_percent.pdf}
        \label{fig:connected_HRR_percent}
    \end{figure}
